---
title: "Funding the War in Ukraine"
subtitle: "How Western Funding Influenced the War in Ukraine"
author: "Bogdan Bunea, Ian Milko, Collin Schwab, and Rayyan Hussien"
date: October 29, 2023
format:
  html:
    code-fold: true
    code-tools: true
    theme: superhero

---

>Read In
```{r}

library(cowplot)
library(tidyverse)
library(viridis)
library(ggrepel)
library(gganimate)
library(magick)
library(here)

equipment <- read.csv(here('data_raw', "FullEquipCas.csv"))
    
glimpse(equipment)
```

>Tanks
```{r}

tanks <- equipment %>% 
    filter(equipment_type == 'Tanks')
```    

::: {.panel-tabset}

## Total Tank Casualties

```{r}

library(tidyverse)

tanks %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>% 
    ggplot(aes(x = Date, y = type_total, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 800,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 2200,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Casualties", title = "Cumulative Russian and Ukrainian Tank Casualties")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')
    
    
```

## Destroyed Tanks

```{r}

tanks %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>% 
    ggplot(aes(x = Date, y = destroyed, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 350,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 1650,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Tanks Destroyed", title = "Cumulative Russian and Ukrainian Destroyed Tanks")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')
    
```

## Captured Tanks

```{r}

tanks %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>% 
    ggplot(aes(x = Date, y = captured, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 100,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 600,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Captured Tanks", title = "Cumulative Russian and Ukrainian Captured Tanks")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')

```



## Abandoned Tanks

```{r}

tanks %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>% 
    ggplot(aes(x = Date, y = abandoned, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 25,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 175,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Tanks Abandoned", title = "Cumulative Russian and Ukrainian Abandoned Tanks")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')

```

:::

The above charts show the differences between Russian and Ukrainian tank casualties over the course of the war. As may be expected, Russia has lost far more tanks than Ukraine. 

>Aircraft (Not including helicopters)

```{r}

aircraft <- equipment %>% 
    filter(equipment_type == 'Aircraft')
    
```

::: {.panel-tabset}


## Total Aircraft Casualties

```{r}

aircraft %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = type_total, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 68,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 100,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Aircraft Casualties", title = "Cumulative Russian and Ukrainian Aircraft Casualties")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')

```

## Destroyed Aircraft

```{r}

aircraft %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = destroyed, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 60,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 90,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Destroyed Aircraft", title = "Cumulative Russian and Ukrainian Destroyed Aircraft")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')

```

## Captured Aircraft

```{r}

aircraft %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = captured, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 1.15,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 0.15,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Captured Aircraft", title = "Cumulative Russian and Ukrainian Captured Aircraft")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')

```

## Abandoned Aircraft

```{r}

aircraft %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = abandoned, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = .25,
             label = 'Ukraine = 0', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = .2,
             label = 'Russia = 0', size = 4, color = 'red') +
    labs(x = "", y = "Total Abandoned Aircraft", title = "Cumulative Russian and Ukrainian Abandoned Aircraft", caption = "A Captain MUST go down with the ship!")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')

```

:::

>Helicopters

```{r}

helicopters <- equipment %>% 
    filter(equipment_type == 'Helicopters')
    
```

::: {.panel-tabset}

## Total Helicopter Casualties

```{r}
    
helicopters %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = type_total, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 20,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 95,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Helicopter Casualties", title = "Cumulative Russian and Ukrainian Helicopter Casualties")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')
    
```

## Helicopters Destroyed

```{r}
    
helicopters %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = destroyed, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 20,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 102,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Destroyed Helicopters", title = "Cumulative Russian and Ukrainian Destroyed Helicopters")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')
    
```

## Helicopters Captured

```{r}
    
helicopters %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = captured, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 3.2,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 1.9,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Captured Helicopters", title = "Cumulative Russian and Ukrainian Captured Helicopters")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')
    
```

## Helicopters Abandoned

```{r}
    
helicopters %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = abandoned, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = .5,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "5/1/2022", y = 1.9,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Abandoned Helicopters", title = "Cumulative Russian and Ukrainian Abandoned Helicopters")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')
    
```

:::


>Naval Ships

```{r}

ships <- equipment %>% 
    filter(equipment_type == 'Naval Ships')
    
```

::: {.panel-tabset}

## Total Ship Casualties

```{r}
    
ships %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = type_total, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 30,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 10,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Ship Casualties", title = "Cumulative Russian and Ukrainian Naval Ship Casualties")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')

```

## Destroyed Ships

```{r}
    
ships %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = destroyed, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 10,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 7,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Destroyed Ships", title = "Cumulative Russian and Ukrainian Destroyed Naval Ships")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')

```

## Captured Ships

```{r}
    
ships %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = captured, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 18,
             label = 'Ukraine', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 1,
             label = 'Russia', size = 4, color = 'red') +
    labs(x = "", y = "Total Captured Ships", title = "Cumulative Russian and Ukrainian Captured Naval Ships")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')

```

## Abandoned Ships

```{r}
    
ships %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = abandoned, color = country, group = country))+
    geom_point()+
    geom_line()+
    annotate(geom = 'text', x = "10/1/2023", y = 2,
             label = 'Ukraine = 0', size = 4, color = 'blue') +
    annotate(geom = 'text', x = "10/1/2023", y = 1,
             label = 'Russia = 0', size = 4, color = 'red') +
    labs(x = "", y = "Total Abandoned Ships", title = "Cumulative Russian and Ukrainian Abandoned Naval Ships")+
    scale_x_discrete(guide = guide_axis(angle = 90))+
    theme_minimal_vgrid()+
    theme(legend.position = 'none')

```
    
:::


>Anti-Aircraft Guns
```{r}

aaguns <- equipment %>% 
    filter(equipment_type == 'Anti-Aircraft Guns')
    
aaguns %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = type_total, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90))  
    
aaguns %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = captured, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90)) 
    
aaguns %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = destroyed, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90)) 
    
aaguns %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = abandoned, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90)) 

```

>Infantry Fighting Vehicles
```{r}

infantry_fighting <- equipment %>% 
    filter(equipment_type == 'Infantry Fighting Vehicles')
    
infantry_fighting %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = type_total, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90))
    
infantry_fighting %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = captured, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90))
    
infantry_fighting %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = destroyed, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90))
    
infantry_fighting %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = abandoned, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90))
```

>Surface to Air
```{r}

s2a <- equipment %>% 
    filter(equipment_type == 'Surface-To-Air Missile Systems')

s2a %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = type_total, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90))    
    
s2a %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = captured, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90))  
    
s2a %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = destroyed, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90))  
    
s2a %>% 
    mutate(Date = fct_inorder(Date, TRUE)) %>%
    ggplot(aes(x = Date, y = abandoned, color = country, group = country))+
    geom_point()+
    geom_line()+
    scale_x_discrete(guide = guide_axis(angle = 90))  

View(s2a)
```

